### 2018-11-22 papers/journal/encoding.tex
Improvements in the reachability section edited slightly

\subsection{The key improvement}
The key improvement in our work over the earlier tool is the
encoding of reachability, which was done using enumeration of paths.
%
In the current work, we have encoded reachability in two different
ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of unreachability.
%
On the other hand,
we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
which needs relatively more auxiliary variables.
%
This is because constraint~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and if we had defined
$r$s in ~\eqref{eq:reach1} without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

@@

\paragraph{$k$-connected property}
%
$k$-connectedness expresses robustness against failure of few edges.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Fail}(d,k)$ encodes that only
existing edges can be failed and exactly $k-1$ edges are failed.
%
$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
%
We use a new variable $r'_{i,j,p}$ to encode reachability from
$i$ to $j$ in at most $p$ steps.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
% \texttt{ReachAbove}(d,r') = &
% \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
\texttt{FReach}(d,r') = &\hspace{-1ex}
\bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
\texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
\end{align*}
%We will be synthesizing $k$-connected graphs.
%
We define $\texttt{Connected}(k)$ that says for all possible valid failures
the graph remains reachable. 
\begin{align*}
\texttt{Connected}(k) = & \forall d.\;
(\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
\land \texttt{Connected}(r'))
% \\
% \texttt{Disconnected}(k) = & \exists d.\;
%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
%                               \land \lnot \texttt{Connected}(r'))
\end{align*}
Since $d$ variables in $\texttt{Connected}(k)$ are universally
quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
%
Therefore, synthesis against this property will require QBF reasoning.
%
We may make the formula quantifier free  by considering all possible failures
separately and introducing a vector of reachability variables for each
failure.
%
However, this will blow up the size of the formula and may not be
solvable by a SAT solver.
%

>>>>

\subsection{The key improvement}
The key improvement of SMT tool over the BMC is the
encoding of reachability, which was done using an enumeration of paths. 
%
In SMT tool, reachability is encoded in two different
ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of unreachability.
%
On the other hand,
we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
which needs relatively more auxiliary variables.
%
This is because constraint~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and if we had defined
$r$s in ~\eqref{eq:reach1} without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

@@

\paragraph{$k$-connected property}
%
$k$-connectedness expresses robustness against failure of few edges.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Fail}(d,k)$ encodes that only
existing edges can be failed and exactly $k-1$ edges are failed.
%
$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
%
We use a new variable $r'_{i,j,p}$ to encode reachability from
$i$ to $j$ in at most $p$ steps.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
% \texttt{ReachAbove}(d,r') = &
% \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
\texttt{FReach}(d,r') = &\hspace{-1ex}
\bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
\texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
\end{align*}
%We will be synthesizing $k$-connected graphs.
%
We define $\texttt{Connected}(k)$ that says for all possible valid failures
the graph remains reachable. 
\begin{align*}
\texttt{Connected}(k) = & \forall d.\;
(\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
\land \texttt{Connected}(r'))
% \\
% \texttt{Disconnected}(k) = & \exists d.\;
%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
%                               \land \lnot \texttt{Connected}(r'))
\end{align*}
Since $d$ variables in $\texttt{Connected}(k)$ are universally
quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
%
%Therefore, synthesis against this property will require QBF reasoning.
%%
%We may make the formula quantifier free  by considering all possible failures
%separately and introducing a vector of reachability variables for each
%failure.
%%
%However, this will blow up the size of the formula and may not be
%solvable by a SAT solver.
%
